Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\subsection{Modeling}
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
\caption{Overview of TSELM.}
\label{cross_attention}
\end{figure}
\subsubsection{Attention Embedding}
After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
learnable embedding tables each with \(K\) entires to embed the 6 layers 
respectively, each resulting in a tensor of shape \(T \times E\). 
After embedding, we follow the same recipe as in \cite{dasb} to 
aggregate the tensor by using attention mechanism to sum all the 6 tensors.

>>>>

\subsection{Modeling}
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
\caption{Overview of TSELM.}
\label{cross_attention}
\end{figure}
\subsubsection{Attention Embedding}
After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
learnable embedding tables each with \(K\) entires to embed the 6 layers 
respectively, each resulting in a tensor of shape \(T \times E\). 
After embedding, we follow the same recipe as in \cite{dasb} to 
aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
keeps the information of each layer while reducing the system complexity by reducing the 
dimension of layers.

\subsubsection{Cross Attention}
The key factor in target speaker extraction is to inject the information of target speaker 
into the mixture. SEF-Net \cite{sef_net} has proposed an embedding free way to inject the 
target speaker information into the mixture by using cross attention module. This approach 
has
